### 2015-02-08 Papers_and_Presentations/presentation/tilePlacement/step9.tex
clean up the home directory of the repository

		%right side row 2
		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw, fill = green] at (8.5,-2) {12\\9.2};
		\node[align=center] at (10,-2) {1.8};

@@

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};

>>>>

		%right side row 2
		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw, fill = green] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw] at (8.5,-2) {12\\9.2};
		% \node[align=center] at (10,-2) {1.8};

@@

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};
		\draw (15.5,-3) -- (15.5,-3.5);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		\node[align=center] at (17,-4.5) {2.6};
